BSOS

### 2014-06-08 Paper.tex
Update Paper.tex
Modified Structure to match formatting

\part{Fundamental Theory of Operating Systems}

\begin{lstlisting}
An Operating System has several different components. All software has to go through the OS in order for the user to be able to utilize any of the hardware. The kernel offers a basic level of control over doing this. The kernel manages memory access for programs in the RAM, determines which programs connect with which hardware, handles the CPU’s operating states, organizes data in the long run, and orders processes in multi-tasking systems. Essentially, the kernel assigns memory space.

                Interrupts are also very important. Interrupts create an efficient way for the OS to interact with its environment. Older systems used to monitor different sources of input for events. Interrupts help automatically save local register contexts and run particular code in response to particular events. Interrupts cause the current program to pause for a moment, save it, and then run code associated with that interrupt. In other words, an interrupt interrupts the program – hence the name, “interrupt”. The kernel handles interrupts.

                Three different types of interrupts are hardware interrupts, software interrupts, and traps. Hardware interrupts may come from a key on a keyboard being hit or the click of a mouse. Software interrupts are generated by programs. Traps come from the CPU itself due to errors or conditions which require the OS for assistance.

                When a computer initially turns on, it runs in supervisor mode. The first programs to run have unlimited access to hardware. When the OS allows another program to take control, the computer transitions into protected mode, where programs’ access to the CPU’s set of instructions is limited. To leave protected mode, an interrupt has to be triggered so that way the kernel will be able to take charge once again.

                An OS manages the interactions between hardware and software on the computer. The most common Operating Systems are Microsoft Windows, Mac OS X, and Linux.
\end{lstlisting}

>>>>

\part{Fundamental Theory of Operating Systems}
\paragraph{Theory}
An Operating System has several different components. All software has to go through the OS in order for the user to be able to utilize any of the hardware. The kernel offers a basic level of control over doing this. The kernel manages memory access for programs in the RAM, determines which programs connect with which hardware, handles the CPU’s operating states, organizes data in the long run, and orders processes in multi-tasking systems. Essentially, the kernel assigns memory space.

\paragraph{Interrupts}
Interrupts are also very important. Interrupts create an efficient way for the OS to interact with its environment. Older systems used to monitor different sources of input for events. Interrupts help automatically save local register contexts and run particular code in response to particular events. Interrupts cause the current program to pause for a moment, save it, and then run code associated with that interrupt. In other words, an interrupt interrupts the program – hence the name, “interrupt”. The kernel handles interrupts.

\paragraph{Types}
Three different types of interrupts are hardware interrupts, software interrupts, and traps. Hardware interrupts may come from a key on a keyboard being hit or the click of a mouse. Software interrupts are generated by programs. Traps come from the CPU itself due to errors or conditions which require the OS for assistance.

\paragraph{Boot}
When a computer initially turns on, it runs in supervisor mode. The first programs to run have unlimited access to hardware. When the OS allows another program to take control, the computer transitions into protected mode, where programs’ access to the CPU’s set of instructions is limited. To leave protected mode, an interrupt has to be triggered so that way the kernel will be able to take charge once again.

\paragraph{Summary}
An OS manages the interactions between hardware and software on the computer. The most common Operating Systems are Microsoft Windows, Mac OS X, and Linux.
